Developing Software Center Using Evolutionary Prototyping Based-on HTML5

### 2014-05-02 Latex/Paper_format.tex
page 4, need testing

\section{Introduction}
% no \IEEEPARstart
Software Center has a function to management software, which adds, removes and update software. Its existence is necessary in all operating systems both desktop and mobile devices. This application use on OpenSUSE, Ubuntu, Mac OS X, Android, iOS, BlackBerry and Windows. However, these applications are not in BlankOn Linux as Indonesian local Linux distribution. Installation of applications in BlankOn Linux currently can be done in the traditional way: first from the console (terminal), thi way can be done if you know the name of the application you want to install the package. The second way to use the Synaptic Package Manager a management application packages. Despite using a GUI (graphic user interface) but still only be done if you know the name of the application you want to install the package and limited its use. Making it difficult for an ordinary user to install the application.

@@

HTML5 is a trend of programming because this technology easy to adapted, can run in many platforms up to desktop utilization [2]. Manokwari Desktop a desktop environment for BlankOn Linux is base on HTML5. Development software center base on HTML5 can run consistent with development of BlankOn Linux [3]. This research tries to make software center HMTL5-based as solution for BlankOn Linux.

@@

\section{HTML5 App in desktop}
run html 5 on dektop need other program, suck webkit to rendering html 5.

\subsection{Webkit and WebkitGTK+}
WebKit is a layout engine software component for rendering web pages in web browsers. It powers Apple's Safari web browser and was previously used in Google's Chrome web browser. Figure 1 and 2 shows how Webkit work.

@@

\subsection{WarSi}
WarSi (Warung aplikasi)
gui from apt command

@@

\subsection{Development Method}
System development methods used in this study is the method of Evolutionary Prototyping. Evolutionary prototyping method has the steps as shown in Figure 3.

@@

Step of Evolutionary Prototyping:
\subsubsection{Initial Consep and requirment}
what konsep

\subsubsection{Quick Desain}

@@

\subsubsection{IF happy, final testing and produck release}

\subsection{UML (Unified Modeling Language}

\subsubsection{Use Case Diagram}
Figure 4 show the use case diagram for software center.

@@

\subsubsection{Activity Diagram}
Figure 5 show activity diagram generaly.

@@

Figure 6 is an activity diagram for a search application. Search Application is divided into two, namely by entering a keyword in the search field and the search for applications by category. Process for Figure 6 are:

@@

Process for Figure 7 are:
\begin{itemize}
\item User select a menu from the main menu next repository, system will display the page repository, there are two options, choose source repository or directly perform the update,
\item User can make changes to the repository by selecting the list
repository that is already available,
\item When the user makes changes to the repository, the system will saved the changes,
\item When the user performs an update to the update repository the repository will be made and the system will display the process update,
\item After update user can upgrade system if available, then the system will display the process upgrade.
\item Process is completed.
\end{itemize}

\subsubsection{Squence Diagram}
(need redraw)

\subsection{Result Development}

\subsection{Testing}
blackbox model
for same hasil (diagram pie)

@@

\section{Conclusion}
The conclusion goes here.

@@

>>>>

\section{Introduction}
% no \IEEEPARstart
Software Center has a function to management software, which adds, removes and update software. Its existence is necessary in all operating systems both desktop and mobile devices. This application use on OpenSUSE, Ubuntu, Mac OS X, Android, iOS, BlackBerry and Windows. However, these applications are not in BlankOn Linux as Indonesian local Linux distribution. Installation of applications in BlankOn Linux currently can be done in the traditional way: first from the console (terminal), this way can be done if you know the name of the application you want to install the package. The second way to use the Synaptic Package Manager a management application packages. Despite using a GUI (graphic user interface) but still only be done if you know the name of the application you want to install the package and limited its use. Making it difficult for an ordinary user to install the application.

@@

HTML5 is a trend of programming because this technology easy to adapted, can run in many platforms up to desktop utilization [2]. Manokwari Desktop a desktop environment for BlankOn Linux is base on HTML5 and GNOME 3. Development software center base on HTML5 can run consistent with development of BlankOn Linux [3]. This research tries to make software center HMTL5-based as solution for BlankOn Linux.

@@

\section{HTML5 App in Desktop}

\subsection{Webkit and WebkitGTK+}
WebKit is a layout engine software component for rendering web pages in web browsers. It powers Apple's Safari web browser and was previously used in Google Chrome web browser. Figure 1 and 2 shows how Webkit work.

@@

\subsection{WarSi}
WarSi (Warung aplikasi) is the name of software center run in BlankOn Linux. It job to help user management applications by make Graphic User Interface. To do management WarSi need link to apt. its use vala programming. Object oriented programming base on c and GObject.

Valac, the Vala compiler, is a self-hosting compiler that translates Vala source code into C source and header files. It uses the GObject type system to create classes and interfaces declared in the Vala source code. The syntax of Vala is similar to C\#, modified to better fit the GObject type system. Vala supports modern language features as the following:

\begin{itemize}
\item Interfaces
\item Properties
\item Signals
\item Foreach
\item Lambda expressions
\item Type inference for local variables
\end{itemize}

Vala is designed to allow access to existing C libraries, especially GObject-based libraries, without the need for runtime bindings. All that is needed to use a library with Vala is an API file, containing the class and method declarations in Vala syntax. Vala currently comes with experimental bindings for GLib and GTK+. It's planned to provide generated bindings for the full GNOME Platform at a later stage.

@@

\subsection{Development Method}
System development methods used in this study is the method of Evolutionary Prototyping. Evolutionary prototyping method has the steps as shown in Figure 4.

@@

Steps of Evolutionary Prototyping:
\subsubsection{Initial Concept and Requirement}

\subsubsection{Quick Design}

@@

\subsubsection{If happy, final testing and product release}

\subsection{UML (Unified Modelling Language}

\subsubsection{Use Case Diagram}
Figure 5 show the use case diagram for software center.

@@

\subsubsection{Activity Diagram}
Figure 6 show activity diagram generally.

@@

Figure 7 is an activity diagram for a search application. Search Application is divided into two, namely by entering a keyword in the search field and the search for applications by category. Process for Figure 6 are:

@@

Process for Figure 8 are:
\begin{itemize}
\item User select a menu from the main menu next repository, system will display the page repository, there are two options, choose source repository or directly perform the update,
\item User can make changes to the repository by selecting the list
repository that is already available,
\item When the user makes changes to the repository, the system will saved the changes,
\item When the user performs an update to the update repository the repository will be made and the system will display the process update,
\item After update user can upgrade system if available, then the system will display the process upgrade.
\item Process is completed.
\end{itemize}

\subsubsection{Sequence Diagram}
(gambar ulang)

\subsection{Result Development}
diisini apa ini?

\subsection{Testing}
Black box testing (also called functional testing) is testing that ignores the internal mechanism of a system or component and focuses solely on the outputs generated in response to selected inputs and execution conditions.[11]

With black box testing, the software tester does not (or should not) have access to the source code itself. The code is considered to be a “big black box” to the tester who cannot see inside the box. The tester knows only that information can be input into to the black box, and the black box will send something back out.

What the test :
Functional include: (list of testing)

after testing to 15 people the result is
(diagram)

@@

\section{Conclusion}
Based on the research that have been carried out during development Software Center using Evolutionary Prototyping HTML5-based, it can be concluded as follows:
\begin{itemize}
\item Analysis and development Software Center that can help users to manage applications in BlankOn Linux has been successfully carried out,
\item In this study the HTML5 programming language can be used for development desktop application,
\item Based on the test results showed that the Software Center can be run on BlankOn Linux.
\end{itemize}.

@@

\bibitem{IEEEhowto:kopka}
IEEE, \emph{IEEE Standard 610.12-1990, IEEE Standard Glossary of Software Engineering Terminology}, 1990.
